\begin{thebibliography}{12}
    \bibitem{Rafiee2021} A. A. Rafiee and M. Farhang, "A deep convolutional neural network for salt-and-pepper noise removal using selective convolutional blocks," \textit{arXiv preprint arXiv:2104.06445}, 2021.
    \bibitem{Zamir2022} S. W. Zamir, A. Arora, S. Khan, M. Hayat, F. S. Khan, and M.-H. Yang, "Restormer: Efficient transformer for high-resolution image restoration," in \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition}, 2022, pp. 1774-1784.
    \bibitem{Wu2022} J. Wu, W. Liu, C. Li, T. Jiang, I. M. Shariful, H. Sun, X. Li, X. Li, X. Huang, and M. Grzegorzek, "A State-of-the-art Survey of U-Net in Microscopic Image Analysis: from Simple Usage to Structure Modification," \textit{Unpublished manuscript}, arXiv:2202.06465, 2022.
    \bibitem{Zhang2017} K. Zhang, W. Zuo, Y. Chen, D. Meng, and L. Zhang, "Beyond a Gaussian denoiser: Residual learning of deep CNN for image denoising," \textit{IEEE Transactions on Image Processing}, vol. 26, no. 7, pp. 3142-3155, 2017.
    \bibitem{Zhang2018} K. Zhang, W. Zuo, and L. Zhang, "FFDNet: Toward a fast and flexible solution for CNN-based image denoising," \textit{IEEE Transactions on Image Processing}, vol. 27, no. 9, pp. 4608-4622, 2018.
    \bibitem{Memis2021} S. Memiş and U. Erkan, "Different adaptive modified Riesz mean filter for high-density salt-and-pepper noise removal in grayscale images," \textit{European Journal of Science and Technology}, no. 23, pp. 359-367, 2021.
    \bibitem{Zhao2017} H. Zhao, O. Gallo, I. Frosio, and J. Kautz, "Loss functions for image restoration with neural networks," \textit{IEEE Transactions on Computational Imaging}, vol. 3, no. 1, pp. 1-11, Mar. 2017.
    \bibitem{Pessoa2023} J. Pessoa, "pytorch-msssim: MS-SSIM for PyTorch," GitHub repository, 2023. Available: \url{https://github.com/jorge-pessoa/pytorch-msssim}.
    \bibitem{Martin01} D. Martin, C. Fowlkes, D. Tal, and J. Malik, "A database of human segmented natural images and its application to evaluating segmentation algorithms and measuring ecological statistics," in \textit{Proceedings of the Eighth IEEE International Conference on Computer Vision (ICCV 2001)}, vol. 2, pp. 416–423, 2001.
    \bibitem{Kodak} R. Franzen, “Kodak lossless true color image suite,” source: http://r0k.us/graphics/kodak, vol. 4, 1999.
    \bibitem{Huang2015} J. B. Huang, A. Singh, N. Ahuja, and M. H. Yang, "Single image super-resolution from transformed self-exemplars," in \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, pp. 5197–5206, 2015.
    \bibitem{Set12} J. Mairal, F. Bach, J. Ponce, G. Sapiro, and A. Zisserman, “Non-local sparse models for image restoration,” in Proc. Int. Conf. Comput. Vis., 2009, pp. 2272–2279.
\end{thebibliography}